Project Notes

### 2020-04-02 notes/notes.tex
Notes: update 02/04/2020

\nocite{*}

@@

@@

@@

On mounting the receive state (which is the actual
transition), check whether there is a message in the 
queue.
\begin{itemize}
\item
If yes -- pop message and call handler based on label
(and cast payload accordingly).

\item
If no -- add handler to queue.
\end{itemize}

On message receive, check whether there are handlers
in the queue. 
\begin{itemize}
\item
If yes -- call the correct one based on
the label (and cast payload accordingly).

\item
If no -- add message to queue.
\end{itemize}

@@

@@

\bibliographystyle{acm}
\bibliography{notes}

>>>>

@@

\subsection{Node}

TODO

\subsection{Browser}

TODO

@@

\texttt{npm test} is already set up -- just need to
set up the Python script to call for testing.

@@

On mounting the receive state (which is the actual
transition), check whether there is a message in the 
queue.
If yes -- pop message and call handler based on label
(and cast payload accordingly).
If no -- add handler to queue.

On message receive, check whether there are handlers
in the queue. 
If yes -- call the correct one based on
the label (and cast payload accordingly).
If no -- add message to queue.

@@

\subsection*{Exception handling}

TODO read Exceptional GV paper \cite{ExceptionalGV}.

@@

\subsection*{Typestate in TypeScript}

Look into TyoeScript transfomers -- the idea is
to define typestate decorators, then augment the
TypeScript compiler to transform the code into some
intermediate layer to perform validation on
typestate: for example, consider the example of a 
stack that can either be full or empty.

\section{Report Structure}

\begin{enumerate}
\item 
Introduction -- as per PLACES (for now)

\item
Background -- process calculus, BST, MPST, code 
generation, TypeScript; think about where React goes?

\item
MPST encoding in TypeScript (section 2 in these notes).
Split into Node and browser targets, also talk about
the different ideas building up to this (pros and
cons of the experiments I did with Calculator in
2019).

Any of the new concepts (exception handling, etc.) will 
go in this section too.

TODO think about how to split into 
more logical sections.

\item
Code generation workflow (section 3 in these notes)
-- software architecture of
toolchain implemented in Python.

\nocite{*}
\bibliographystyle{acm}
\bibliography{notes}
